Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-27 robdml.tex
tex

% 1. possible combinations

Although any of the existing triplet sampling strategies, such as Random,
Semihard~\cite{facenet}, Softhard~\cite{revisiting},
Distance-weighted~\cite{distance}, and the within-batch Hardest negative
sampling method, can be selected for source hardness $H_\mathsf{S}$ and
destination hardness $H_\mathsf{D}$, not all combinations are effective and
efficient.
%
In this subsection, we find a proper combination empirically as a baseline for
further experiments.

% 2. sort sampling strategies

As HM is expected to increase the hardness of the source triplet, we first sort
the triplet sampling methods according to their approximated mean hardness of
$1000$ mini-batches from CUB dataset with an imagenet-initialized RN18 model,
as shown in~\cref{tab:hsort}.
%
Then we adversarially train models on the CUB dataset with all possible
combinations, and summarize their R@1 and ERS performance in \cref{tab:desth}.

>>>>

% where to start

To validate the effectivenss of HM, we start from using the hardness of another
benign triplet sampled with a different triplet sampler as $H_\mathsf{D}$, as
the existing triplet samplers are known not to result in model collapse in
regular training.

% combinations

Due to the flexibility of HM, any of the existing (and future) triplet samplers
can be used for calculating $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
But not all possible combinations are expected to be effective or efficient in
terms of adversarial training, as the \emph{source} hardness of a notable
portion of the given triplets should be increased.
%
Thus, we first sort the existing samplers, namely Random,
Semihard~\cite{facenet}, Softhard~\cite{revisiting},
Distance-weighted~\cite{distance}, and the within-batch Hardest negative
sampler, based on the approximated mean hardness of their outputs, as shown
in~\cref{tab:hsort}.
%
Then we adversarially train models on the CUB dataset with all combinations
respectively, and summarize the R@1 and ERS performance in \cref{tab:desth}.
